---
title: "Code Sample Submission"
author: "Michelle Shames"
date: today 
format:
  html:
    toc: true
    embed-resources: true
    code-fold: show
    link-external-newwindow: true
execute:
  warning: false 
from: markdown+emoji
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup
#| echo: FALSE

# Packages
library(tidyverse) 
library(scales)
```

## I. PROJECT BACKGROUND
### 1.1 Motivations
### 1.2 Methods
#### Data & Sample
```{r}
#| label: sample-n
#| echo: FALSE

sample_n <- 26000 
```


The sample of `r scales::comma(sample_n)` unique complain allegations includes ...

#### Research Design

### 1.3 Analyses & Key Findings

### 1.4 Future Research

:::{.callout-warning collapse=true}
## Disclaimer 
This research project is ongoing. Upon completion of the research, I hope to share the database publicly. 
:::

## II. ABOUT THE CODE SAMPLE
This code sample consists of excerpts from various stages of the research and analysis process. Further code will happily be provided upon request. *Please note, some outputs are suppressed due to confidentiality.*   

**This document was created and rendered using Quarto, the code for which is available in [my code sample GitHub repository here](https://github.com/m-shames/portfolio/tree/d5e6880052aa5cb09a713dea4fdc04fa8d3f0f4c/2_police-oversight).**

## III. CODE SAMPLE

